Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction

### 2019-11-22 docs/article.tex

\section{Results}
	\par The classifiers used 
discrim analysis
decision tree
naive bayes

Acurácia média de classificação: 0.763232
Acurácia média de classificação: 0.720606
Acurácia média de classificação: 0.676566
lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

>>>>

\section{Results}

lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,
